---
title: "CPR Ocean Plastics Explorer"
resource_files:
- data/data.RDS
- R/setup.R
- R/controls.R
- R/boxplots.R
- R/histogram.R
- R/incid_start.R
- R/incid_end.R
- R/incid_path.R
- R/timeline_start.R
- R/timeline_end.R
- R/timeline_path.R
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    navbar:
    - align: right
      href: mailto:keith.mcnulty@gmail.com
      icon: fa-envelope
      title: Contact App Author
    - href: https://github.com/keithmcnulty/cpr_data
      icon: fa-github
      title: View Code
    - align: right
      href: http://twitter.com/share?url=https://keith-mcnulty.shinyapps.io/cpr_explorer
      icon: fa-twitter
      title: Share
    orientation: rows
    theme: cerulean
    vertical_layout: scroll
---

```{r setup, include = FALSE, code = readLines('R/setup.R')}

# basic settings and data load

```






Sidebar {.sidebar data-width=300} 
===============================================


<br>
This app allows you to view incidences of man-made plastics discovered in Continuous Plankton Recorders (CPRs) towed in the North Atlantic, Arctic and European Waters.  CPRs have been towed through these waters since the 1930s, but the first incident of man-made plastic interference was recorded in 1957.
<br><br>
This app allows you to view some simple statistics about these incidents, as well as visualize the location, timeline and basic information on each incident.  For more information on the CPR study see the recent paper in <a href="https://www.nature.com/articles/s41467-019-09506-1">Nature</a>, which contains a link to the data used for this app.
<hr>
Filters can be applied below for all analyses conducted in this app.  <b>Note:</b> When viewing Timelines, ensure to select filters <i>before</i> pressing play.

<br>

``` {r controls, code = readLines('R/controls.R') }

# sidebar UI controls


```



View statistics
===============================================

Row
---------------------------------------

### Incident boxplots

``` {r generate incident boxplots, code = readLines('R/boxplots.R')}

# generate incident boxplots

```


Row
--------------------------------------

### Incident density histogram

``` {r generate incident density histogram, code = readLines('R/histogram.R')}

# generate incident density histogram

```



View Incidents
===============================================


Row {.tabset .tabset-fade data-height=700}
-----------------------------------------------

### Incidents by tow start point

``` {r generate starting point view, code = readLines('R/incid_start.R')}

# generate view by incident start

```

### Incidents by tow end point

``` {r generate end point view, code = readLines('R/incid_end.R')}

# generate view by incident end

```




View Timeline 
===============================================



Row {.tabset .tabset-fade data-height=700}
-----------------------------------------------

### Timeline by tow start point

``` {r generate timeline starting point view, code = readLines('R/timeline_start.R')}

# generate animated timeline by start point

```


### Timeline by tow end point

``` {r generate timeline end point view, code = readLines('R/timeline_end.R')}

# generate animated timeline by end point

```


